JD notes on effects

### 2022-07-01 manuscript/body.tex
Moved Jensen's stuff up

\NEW{It is usually important to report the estimates that reflect the expected values of the untransformed response. This is not a major issue in simple linear models. However, when dealing with nonlinear link functions,  generated predictions may not reflect the observed response due to the bias in the expected mean induced by the nonlinear transformation of the response variable -- a consequent of Jensen effect mentioned above. In such cases, bias correction is needed to back-transform the predictions to the original scales. The common approach for bias-adjustment is second-order Taylor approximation \citep{duursma2003bias, hanmer2013behind}; already implemented in \pkg{emmeans} \citep{lenth2018package}. Here, we describe and implement a different approach -- whole-sample-based approach for bias correction.}

>>>>

\NEW{It is usually important to report the estimates that reflect the expected values of the untransformed response. This is not a major issue in simple linear models. However, when dealing with nonlinear link functions,  generated predictions may not reflect the observed response due to the bias in the expected mean induced by the nonlinear transformation of the response variable -- a consequent of Jensen effect mentioned above. In such cases, bias correction is needed to back-transform the predictions to the original scales. The common approach for bias-adjustment is second-order Taylor approximation \citep{duursma2003bias, hanmer2013behind}; already implemented in \pkg{emmeans} \citep{lenth2018package}. Here, we describe and implement a different approach -- whole-sample-based approach for bias correction. Hammer and Kalkan \citep{hanmer2013behind} introduced mean- and whole-sample- based approaches but limited their discussion to binary response models only.}
